Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-28 manuscript/main.tex
typo in manuscript

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $1.24 * 10^11$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
documents that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000.\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation
(\url{https://www.elastic.co/guide/en/elasticsearch/reference/current/query-dsl-mlt-query.html} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}

>>>>

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $1.24 * 10^{11}$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
documents that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000.\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation
(\url{https://www.elastic.co/guide/en/elasticsearch/reference/current/query-dsl-mlt-query.html} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}
